### 2021-04-06 papers/SYRCoSE/regmachine-eventstruct.tex
SYRCoSE: proof sketch

$$ e_1 \primcfRel e_2 \iff e_1 \neq e_2 \wedge f_{\lfPO}(e_1) = f_{\lfPO}(e2) $$

@@

%% I can't use `proof` here, sorry.  
% \begin{proof}
% \end{proof}

\todo{Sketch the proof if we'll have space and time}

>>>>

$$ e_1 \primcfRel e_2 \iff e_1 \neq e_2 \wedge \lfPO(e_1) = \lfPO(e2) $$

@@

We sketch the proof below.

First, we need to show that $\caOrd \ \defeq \ (\lPO \cup \lRF)^*$
is a partial order. Reflexivity and transitivity follows immediately 
from the definition of the reflexive-transitive closure. 
To show antisymmetry note that $\lessdot_{\lPO} \subseteq \identOrd$
and $\lessdot_{\lRF} \subseteq \identOrd$ by construction. 
Therefore $\caOrd \subseteq \identOrd$. Since $\identOrd$ is
partial order, it is antisymmetric, and thus $\caOrd$ should also be antisymmetric.
The axiom of finite cause, \ie $\prefix{e}$ is finite for every event $e$, 
follows from the fact that at each step of the construction 
the set of possible predecessors of the new event 
can be over-approximated by the finite sequence $\eventSeq$.

Second, we need to show that the conflict relation defined as 
$ e_1 \primcfRel e_2 \iff e_1 \neq e_2 \wedge \lfPO(e_1) = \lfPO(e2) $
obeys the laws of primitive conflict relation. 
Trivially, this relation is irreflexive, symmetric, and transitive.
Also, it is easy to see that it satisfies choice-locality. 
The side condition $\neg (e_{\lPO} \cfRel e_{\lRF})$ of the rule \ESLoadRule
ensures that the primitive conflict relation would not violate 
hereditary property.
